Bootstrapping-naiveBayes

### 2020-11-03 DATA622/M09-Bootstrap-CrossValidation-NaiveBayes.RMD
Updated M09

```{r}
library('e1071')
file<-'c://Users/rk215/Data/heart.csv'
heart<-read.csv(file,head=T,sep=',',stringsAsFactors=F)
head(heart)
catheart<-heart[,c(2,3,6,7,9,11,12,13,14)]

>>>>

```{r}
library('e1071')
file<-'heart.csv'
heart<-read.csv(file,head=T,sep=',',stringsAsFactors=F)
head(heart)
catheart<-heart[,c(2,3,6,7,9,11,12,13,14)]
